---
title: "Group Assignment XX"
author:
    - Research in Social Media @ TiSEM
date: "Block 4, 2021"

duedate: "1st of May, 2021"
duetime: "23:45 CET"

fontfamily: mathpazo
fontsize: 11pt
header-includes:
   - \linespread{1.05}
output:
  #- unilur::tutorial_pdf_solution
  #- unilur::tutorial_pdf
  - unilur::answer_rmd
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

\hrulefill

## Instructions

This group assignment is due on the **`r rmarkdown::metadata$duedate`** at **`r rmarkdown::metadata$duetime`**.

Solutions should be turned in via GitHub Classroom.^[
  Review the [tutorial](INSERT_LINK) for how to accept the group assignment from GitHub.
]
**Only most recent commit on the master branch when the assignment is due will be graded**.
Your solution must use the `Rmarkdown` template provided in the assignment's repository that you cloned for this assignment. 
Failure to do so will result in a assignment grade of **zero**.
Refer to the repository's `README.md` for instructions on how to complete the title and author fields for submission.

Remember, your goal is to communicate. 
Full credit will be given only to the correct solution which is described clearly. 
Convoluted and obtuse descriptions might receive low marks, even when they are correct. 
Also, aim for concise solutions, as it will save you time spent on write-ups, and also help you conceptualize the key idea ofthe problem.

\medskip

\hrulefill

## Part I - XXX

- An Example Question

```{r, solution = TRUE}
#an example solution
mean(cars$speed)
```

\newpage

## Part II - Something

## Part III - Something

## Part IV - Something

